Cognate beginnings to bilingual lexical acquisition

### 2024-01-15 manuscript/manuscript.tex

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, boxrule=0pt, enhanced, breakable]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, breakable]}{\end{tcolorbox}}\fi
